Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-23 paper/paper-mainfile.tex

\nocopyright
%
% PDF Info Is REQUIRED.
% For /Title, write your title in Mixed Case.
% Don't use accents or commands. Retain the parentheses.
% For /Author, add all authors within the parentheses,
% separated by commas. No accents, special characters
% or commands are allowed.
% Keep the /TemplateVersion tag as is
\pdfinfo{
/Title (Transforming Partially Ordered HTN Problems to Totally Ordered)
/Author (Anonymous)
/TemplateVersion (2022.1)
}

@@

%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\iffalse
\title{Transforming Partially Ordered HTN Problems to Totally Ordered}
\author {
    % Authors
    Anonymous

@@

\title{Transforming Partially Ordered HTN Problems to Totally Ordered}

>>>>

\nocopyright
%
% PDF Info Is REQUIRED.
% For /Title, write your title in Mixed Case.
% Don't use accents or commands. Retain the parentheses.
% For /Author, add all authors within the parentheses,
% separated by commas. No accents, special characters
% or commands are allowed.
% Keep the /TemplateVersion tag as is
\pdfinfo{
/Title (Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
Planning Problems is Half the Job (to Getting them Solved More Efficiently))
/Author (Anonymous)
/TemplateVersion (2022.1)
}

@@

%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\iffalse
\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
\author {
    % Authors
    Anonymous

@@

\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
